Modeling thermal dust emission in the {\it PLANCK} 2015 release maps

### 2015-06-21 ms.tex
more detailed outline of intro with some actual text

Based on the \PLANCK~2015 data release maps \citep{planck2015}, we present a 
thermal dust emission analysis analogous to that of \cite{meisner15}. We 
isolate thermal dust emission in the \PLANCK~frequency maps, and present 
full-sky models of the unpolarized thermal dust emission using several 
paremeterizations of the dust spectrum, including single modified blackbody and
two-component models. The qualitative conclusions of \cite{meisner15} remain 
unchanged. In particular, the zodiacal light still represents the dominant 
systematic problem of our dust model on large angular scales, and the cosmic 
infrared background anisotropy remains the dominant systematic problem on small
angular scales.

@@

\section{Introduction}
% brief importance of dust
% iras first revolution in mapping ISM cirrus
% planck more recent breakthrough in mapping dust emission due to high
%     angular resolution / sensitivity of broad range of frequencies
% mention the existing dust data products, say they're all very useful for
%     many purposes
% but say that they all still are not perfect, and we want to investigate
%     what effect swapping in the latest planck release has on the dust model
% and we also just want to have a model with data from latest Planck release,
%     which has never been done by anyone before

% list of the sections

>>>>

Based on the \PLANCK~2015 data release maps \citep{planck2015}, we present a 
thermal dust emission analysis analogous to that of \cite{meisner15}. We 
isolate thermal dust emission in the \PLANCK~2015 frequency maps, and present 
full-sky models of the unpolarized thermal dust emission using several 
paremeterizations of the dust spectrum, including single modified blackbody and
two-component models. The qualitative conclusions of \cite{meisner15} remain 
unchanged. In particular, the zodiacal light still represents the dominant 
systematic problem of our dust model on large angular scales, and the cosmic 
infrared background anisotropy remains the dominant systematic problem on small
angular scales.

@@

\section{Introduction}
% brief importance of dust
Interstellar dust in our Galaxy represents a crucial and pervasive foreground
for astronomical observations over an extremely wide range of photon energies.
In the optical, ultraviolet and near-infrared, extinction by intervening dust
attenuates and reddens the observed signal from background stars, galaxies and
transients. At millimeter wavelengths, thermal dust emission contaminates
observations of the cosmic microwave background (CMB).

% iras first revolution in mapping ISM cirrus
While the dust in general lies within a disk a few hundred parsecs in scale 
height centered about the Galactic midplane, its detailed distribution is very 
patchy and cloudlike, as first revealed in far-infrared thermal emission by the
groundbreaking IRAS mission. Thus, it is of great importance to map 
interstellar dust over the entire sky, with high angular resolution and 
sensitivity.

% planck more recent breakthrough in mapping dust emission due to high
%     angular resolution / sensitivity of broad range of frequencies
The Planck mission (cite 2013 and 2015 release overview papers) has recently 
provided a breakthrough in full-sky mapping of emission from interstellar dust,
by obtaining relatively artifact free full-sky maps at XX frequencies from QQ 
to PP GHz, with a superb combination of near-IRAS resolution from QQ-PP and 
high sensitivity. Although these \PLANCK~maps contain various emission 
components, including the CMB, zodiacal light,and molecular emission, it is 
nevertheless possible to isolate exquisite maps of thermal emission from 
interstellar dust grains.
% mention the existing dust data products, say they're all very useful for
%     many purposes
Several full-sky data products currently exist for predicting emission and/or
extinction by interstellar dust. SFD - mention DIRBE temperature limitation.
Planck allows us to get around temperature limitation. One sentence overview of
Planck team's model. One or two sentences about Meisner+Finkbeiner modeling.

% but say that they all still are not perfect, and we want to investigate
%     what effect swapping in the latest planck release has on the dust model
% and we also just want to have a model with data from latest Planck release,
%     which has never been done by anyone before
But none of these are yet perfect. Mention CIBA and zodi as examples from
Meisner + Finkbeiner. Also, no Planck 2015 release thermal dust model yet
exists at all.

% list of the sections
Much of our detailed methodology is identical to that of Meisner/Finkbeiner 
2015. As a result, throughout this paper, we mainly emphasize any notable 
differences relative, and otherwise refer the reader to Meisner/Finkbeiner 
2015 for thorough details.
